---
title: "Script (Data Compilation + Analysis)"
author: "Erik Curtis"
date: "2024-05-30"
output: html_document
---

# 1. Prepare Data

Here we clean our data and prepare dataframes/.csv files for statistical analysis. This section takes the raw data from the ddPCR plate files ("/Data" directory) and separates it into 4 .csv's

1.  LeafMesos-BKD.csv (Background samples from mesocosms pre-release)
2.  LeafMesos-Controls.csv (Field blanks, Extraction blanks, and +/- PCR controls)
3.  LeafMesos-ReleaseSolution.csv (eDNA source solution / buckets)
4.  LeafMesos-Mesoscosms.csv (the release data)

In addition, this script incorporates additional relevant data from the experiment, drawn from the "/Files" directory. This includes the volume of water filtered from each sample, as well as ancillary data (Temp, pH, water velocity, nutrient conc., etc.)

```{r Directory + Packages}
knitr::opts_chunk$set(echo = TRUE)
rm(list=objects())
this.dir = dirname(rstudioapi::getActiveDocumentContext()$path)
data.dir = paste0(this.dir,"/Data")
files.dir = paste0(this.dir,"/Files")
plots.dir = paste0(this.dir,"/Plots")
setwd(this.dir)

#Packages
library(dplyr)
library(ggpubr)
library(ggsci)
library(Rcpp)
library(reshape)
library(lubridate)
library(naniar)
library(gtools)
library(tidyr)
```

Here, we prepare the raw data (.csv files obtained from the ddPCR machine) for analysis. Positive and negative controls are separated from experimental data, and reactions that failed (i.e. not enough separation between positive and negative droplet clouds) are removed.

```{r Prep Data}
#Create a blank dataframe
Data.Full = data.frame(matrix(nrow= 0, ncol =0))

#Load Data into Data.Full
 
list = list.files(data.dir)
list <- mixedsort(sort(list))
for (i in 1:length(list)) {
  Data.Full <-rbind(Data.Full, read.csv(paste0(data.dir,"/",list[i]) , row.names = ) %>% mutate(Run = i))
}

#Remove unnecessary columns from Quantasoft outputs
Data.Full <- Data.Full %>% select(-c(2,3,5,7,9,11:14,17:21,23:41,43:63))

#Remove failed wells (identified manually by looking at 1-D plot in QuantaSoft)
#Failed reactions are identified by the plate number, and the well coordinates
failed.Rxns <- c("1.F01", "1.F02", "1.F03", "7.C02", "7.C02", "8.C07", "8.C08",
                 "8.C09", "8.F04", "8.F05", "8.F06", "8.C07", "8.C08", "8.C09",
                 "9.B10", "9.B11", "9.B12", "10.C01", "10.C02","10.C03", "10.G04",
                 "10.G05", "10.G06", "10.C10", "10.C11", "10.C12", "10.D10",
                 "10.D11", "10.D12", "14.E07", "14.E08", "14.E09", "16.A04",
                 "16.B04", "16.C04", "18.B06", "18.C05", "18.C06", "18.D06",
                 "18.E05", "18.H04", "16.A01", "16.A02", "16.A03", "16.B01",
                 "16.B02", "16.B03", "14.C07", "14.C08", "14.C09")  
Data.Full <- Data.Full %>% mutate(Run.ID = paste(as.character(Run),Well,sep="."))
Data.Full <- Data.Full %>% replace_with_na(list(Run.ID = failed.Rxns))
Data.Full <- Data.Full %>% na.omit()
Data.Full <- Data.Full %>% select(-c(11))


#Separate experimental data from negative and positive controls
#Information about each ddPCR reaction is encoded in "Sample"
Data.NC <- Data.Full %>% 
  subset(Sample != "Negative_CTL") %>% 
  subset(Sample!= "Positive_CTL") %>% 
  subset(substr(Sample,1,2) != "EB") %>% 
  subset(substr(Sample,1,2) != "CB")

Data.C <- Data.Full %>% 
  subset(Sample == "Negative_CTL" |
         Sample == "Positive_CTL" | 
         substr(Sample,1,2) == "EB" | 
         substr(Sample,1,2) == "CB")

#Data about the sample is encoded in its name

Data.NC <- Data.NC %>% 
  cbind(colsplit.character(Data.NC$Sample,
                           split="_", 
                           names = c("Meso.Num", "Time", "Size","Dilution")
                           )
        ) %>% 
  suppressWarnings()

#Separate the release solution from sample data

#BKT = Release Solution/Bucket Data
Data.BKT <- subset(Data.NC, Time == "CARP" | Time == "STHD") 
#NC = Not Control (i.e. sample data)
Data.NC <- subset(Data.NC, Time != "CARP" & Time != "STHD")

#Correct dilution factor for samples that were not diluted, replace with "1"
rem <- c("M1","M2","M3","M4","M5","M6",
         "M7","M8","M9","M10","M11","M12",
         "M13","M14","M15","M16","M17","M18",
         "M19","M20","M21","M22","M23","M24")
Data.NC <- Data.NC %>% 
  replace_with_na(list(Dilution = rem),"1x") 

x <- Data.NC %>% 
  subset(is.na(Dilution)) %>% 
  mutate(Dilution = "1")

Data.NC <- Data.NC %>% subset(!is.na(Dilution))
Data.NC <- rbind(Data.NC, x)
rm(x)

#Some samples were diluted prior to ddPCR, so we need to scale their concentration accordingly.
#We do this by multiplying by the dilution factor
Data.NC <- Data.NC %>% mutate(Concentration = Concentration * as.double(Dilution))

#Combining Technical Replicates

#We ran each mesocosm sample in triplicate, and we want to combine these 3 values into a single value for concentration. 
#We do this by summing the positive and negative droplets for all 3 ...

x <- Data.NC %>% 
  group_by(Sample, Target) %>% 
  dplyr::summarize(Well = "*", 
            Target = first(Target),
            CopiesPer20uLWell = mean(CopiesPer20uLWell), 
            Positives = sum(Positives), 
            Negatives= sum(Negatives), 
            AcceptedDroplets = sum(AcceptedDroplets), 
            Threshold = mean(Threshold), 
            Run = first(Run), 
            Dilution = first(Dilution)
            ) %>% 
  suppressMessages()

#Now we calucate concentration from the PDF of the Poisson Distribution 
#Quantasoft applies this formula to each well to obtain the estimate for concentration; here we apply it to the sum of three wells
#In this formula, 0.000848 uL is the average volume of a droplet during ddPCR (Given by Quantasoft)
 
x <- x %>% 
  mutate(Concentration = -log(Negatives/AcceptedDroplets)/0.000848)
#Units for Concentration are gene copies per uL

#Separate "Sample" again and fix dilution
x <- x %>% 
  cbind(colsplit.character(x$Sample, 
                           split="_", 
                           names = c("Meso.Num", "Time", "Size")
                           ) 
        ) %>% 
  suppressWarnings()
x <- x[-c(15)]
x$Dilution <- as.numeric(x$Dilution)
x <- x %>%  mutate(Concentration = Concentration*Dilution)

#Recombine
Data.NC <- x

#Truncate concentration to 2 decimal places
Data.NC$Concentration <- Data.NC$Concentration %>% 
  round_any(accuracy = 0.01, f=floor)

#Filter out BKD samples

#BKD = Background data, i.e. samples taken prior to eDNA addition
Data.BKD <- Data.NC %>% subset(Time == "BKD")
#NC = Not Control (i.e. samples taken after eDNA addition)
Data.NC <- Data.NC %>% subset(Time != "BKD")


#Get volume filtered for each sample 
Vol.Filtered <- read.csv(paste0(files.dir,"/FilteredVolume.csv"))
Data.NC <- inner_join(Data.NC, Vol.Filtered, by=c('Meso.Num','Time','Size'))

#Calculate the eDNA conc. in the water sample (GC.mL) given the concentration in the ddPCR reaction (Concentration, in GC / uL)
#DNA from the sample is eluted in 50uL of buffer 
# 4uL of this eluted DNA is added to 16 uL supermix (20 uL total rxn mixture)
# After algebra, calculation is the following 

Data.NC <- Data.NC %>% 
  mutate(GC.mL = Concentration*250 /Vol.Filtered.mL)

#Get mesocosm volume + ancillary for each mesocosm
#This datasheet contains DOC, Temp, pH, turbidity, and most importantly, Mesocosm Volume for each time point
Vol.Meso <- read.csv(paste0(files.dir,"/AncillaryFULL.csv"))
Data.NC <- inner_join(Data.NC,Vol.Meso, by=c("Meso.Num","Time"))


#Multiply GC.mL (concentration data) with Mesocosm volumes to get total number of gene copies in each mesocosm (count data)
Data.NC <- Data.NC %>% mutate(Gc.mesocosm = GC.mL * Meso.Volume.mL)

#Now adjust for diluted samples in release solution data
Data.BKT <- Data.BKT %>% 
  dplyr::rename(Bucket = Meso.Num, Rel.soln = "Time")

X <- Data.BKT$Dilution
Data.BKT$Dilution <- X %>%
  replace(X == "BKT1"| X == "BKT2" | X =="BKT3" | X =="BKT4", "1")
rm(X)

#Adjust Concentration by dilution factor
Data.BKT <- Data.BKT %>% 
  mutate(Concentration = Concentration * as.double(Dilution))

#Ignore Carp in STHD buckets and Steelhead in Carp Buckets (usually below LOD anyway)
#Also remove run 15, samples needed diluting, positive cloud was too dense
Data.BKT <- Data.BKT %>% subset(Target == Rel.soln & Run != 15 & Run != 13)

#Calculate true concentration (Vol. Filtered was 100mL for every sample)
Data.BKT <- Data.BKT %>% mutate(GC.mL = (Concentration*1000)/(4*100))

#Export everything as .csv files to "Files" directory
?write.csv
write.csv(Data.BKD, paste0(files.dir,"/LeafMesos-BKD.csv"))
write.csv(Data.C, paste0(files.dir,"/LeafMesos-Controls.csv"))
write.csv(Data.BKT, paste0(files.dir,"/LeafMesos-ReleaseSolution.csv"))
write.csv(Data.NC, paste0(files.dir,"/LeafMesos-Mesoscosms.csv"))
```

# 2. Data Analysis + Figure Generation

Import packages, function definitions, color schemes, and themes for ggplot2 objects.

```{r Directories + Packages}
library(ggplot2)
library(plyr)
library(dplyr)
library(grid)
library(tidyverse)
library(GGally)
library(Hmisc)
library(stats)
library(emmeans)
library(ggpubr)
library(lme4)
library(rstatix)
library(ggResidpanel)
library(PCAtools)
library(lmerTest)
library(colourpicker)
library(ggsignif)
library(MuMIn)
library(lmtest)
library(vegan)
library(gcookbook)
library(ggfortify)
library(patchwork)
library(car)
library(gridExtra)
library(magrittr)
rm(list=objects())

this.dir = dirname(rstudioapi::getActiveDocumentContext()$path)
data.dir = paste0(this.dir,"/Data")
files.dir = paste0(this.dir,"/Files")
plots.dir = paste0(this.dir,"/Plots")
setwd(this.dir)

#Functions
#This function colors the facets of a ggplot2 object
facetColor <- function(plot,colors) {
  g <- ggplot_gtable(ggplot_build(plot))
  strip_both <- which(grepl('strip-', g$layout$name))
  fills <- colors
  k <- 1
  for (i in strip_both) {
    j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
    k <- k+1
  }
  grid.draw(g)
  
  return(g)
}

## Annotation Function for plotting inset graphs
annotation_custom2 <- function (grob, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, data) 
{
  layer(data = data, stat = StatIdentity, position = PositionIdentity, 
        geom = ggplot2:::GeomCustomAnn,
        inherit.aes = TRUE, params = list(grob = grob, 
                                          xmin = xmin, xmax = xmax, 
                                          ymin = ymin, ymax = ymax))
}

#Themes
#Color palette 
p1 <- c("gray81","#bdd7e7","#2171b5","#6baed6")
p2 <- c("#f08080","#f4978e","#f8ad9d","#fbc4ab")
p3 <- c("#dee2e6","#adb5bd","#495057","#212529",
        "red","maroon","magenta","lavender")
p4 <- c("#B7ECFF","#E8CDE9","#A0ABB2","#CDA969",
        "#fcca46","#fe7f2d","#a1c181","#618f9b")
p5 <- c("#A0ABB2","#CDA969","#fcca46","#fe7f2d","#a1c181",
        "#618f9b","#f08080","#f4978e","#f8ad9d","#fbc4ab")
p6 <- c("#A0ABB2","#CDA969","#fcca46","#fe7f2d",
        "#a1c181","#618f9b","#B7ECFF","#E8CDE9")
p7 <- c("#A0ABB2","#CDA969","#fcca46","#fe7f2d","#a1c181","#618f9b")
p7.5 <- c("#89959c", "#b29155", "#e3b238", "#e76c1f", "#91aa73", "#547785")
p8 <- c("#C5C7C9","#D9C196","#F0D27F","#F5985A","#B5C7A3","#79A7B3")
p8.5 <- c("#E0E2E4", "#F3DDB1", "#FFEB9D", "#FFB782", "#D0E3BC", "#9ECBD7")
p9 <- c(p7,p8)
p9.5 <- c(p7.5, p8.5)
p10 <- c("gray81","thistle1","mediumpurple1","darkorchid2")
p11 <- c("#009AD0","#B7ECFF","#BD62CC","#E8CDE9")

#Themes

```

Import and prepare data.

```{r Step 1}
#Load datafile   
Mesos <- read.csv(paste0(files.dir,"/LeafMesos-Mesoscosms.csv"))
Mesos <- Mesos[-1]

# Cast columns to factors
Mesos$Time <- as.factor(Mesos$Time)
Mesos$Size <- as.factor(Mesos$Size)
Mesos$Row <- as.factor(Mesos$Row)
Mesos$Treatment <- as.factor(Mesos$Treatment)

#Remove Mesocosm 15, too many issues in droplet cloud separation. 
#Probably an extraction issue? Dust/particles in the samples?
#Could also be an inhibition issue.
Mesos <- Mesos %>% subset(Meso.Num != "M15")

#Remove any 0's (or below LOD) to their own df for later
#LOD is 3.8 GC/rxn for Carp and 3.2 GC/rxn for Steelhead
Mesos.Full <- Mesos

Mesos.Zeros <- Mesos %>% 
  subset(GC.mL == 0 |
           (Target=="CARP" & CopiesPer20uLWell < 3.8) |
           (Target=="STHD" & CopiesPer20uLWell < 3.2)
         )

Mesos <- Mesos %>% 
  subset(GC.mL != 0 & ((Target=="CARP" & CopiesPer20uLWell > 3.8) |
                         (Target=="STHD" & CopiesPer20uLWell > 3.2)) 
         )

#Calculate LN for all GC.meso 
Mesos$LNGc.meso = log(Mesos$Gc.mesocosm)

#Set orders
Mesos$Treatment = factor(Mesos$Treatment, 
                         levels=c("ETO", "DOC","NCL","NCH","BFL","BFH"))

### Export Slope Data ----
X <- Mesos %>%
  group_by(Meso.Num, Row, Target, Treatment, Size) %>%
  do({
    mod = lm(LNGc.meso ~ Time.hr, data = .)
    data.frame(K = coef(mod)[2] *24)
  }) 
depthkey <- Mesos %>% 
  group_by(Meso.Num) %>% 
  dplyr::summarise(depth = mean(depth.m))
X$Trtmt <- X$Treatment
X = subset(X,select = -Treatment)
X <- inner_join(X, depthkey, by= "Meso.Num")

X <- X %>% mutate(K_s = K / 86400)
X <- X %>% mutate(V_dep = K_s * depth * 1000)
write.csv(X, paste0(files.dir,"/MesosRemovalRAW.csv"), row.names = FALSE)

Raw <- X %>% 
  group_by(Trtmt) %>% 
  dplyr::summarise(Removal = mean(K), se = sd(K)/sqrt(n())) %>%
  suppressMessages()
  
Raw_Size <- X %>% 
  group_by(Trtmt,Size,Target) %>% 
  dplyr::summarise(Removal = mean(K), se = sd(K)/sqrt(n())) %>%
  suppressMessages()

# For values below the LOD, set conc. to 1/2 the limit of detection.
# These values represent a small proportion of the total data, so we excluded them from the statistical analyses
Mesos.Zeros <- Mesos.Zeros %>% 
  mutate(Gc.mesocosm = ifelse(Target == "CARP", 0.475*Meso.Volume.mL, 0.4*Meso.Volume.mL))
Mesos.Zeros$LNGc.meso = log(Mesos.Zeros$Gc.mesocosm) 
Mesos.Zeros$Well <- factor(Mesos.Zeros$Well, levels = c("*","%"))

# Here we calculate the proportion of each size class within a sample
Mesos.Sum <- rbind(Mesos[c(1:36)], Mesos.Zeros) %>% 
  group_by(Time, Target, Meso.Num) %>% 
  dplyr::summarise(n = sum(Gc.mesocosm)) %>% 
  suppressMessages()
Mesos.prop <- inner_join(rbind(Mesos[c(1:36)], Mesos.Zeros), Mesos.Sum, by=c("Time","Target","Meso.Num"))
Mesos.prop <- Mesos.prop %>% mutate(prop = Gc.mesocosm / n)
#Set order of treatment variables
Mesos.prop$Treatment = factor(Mesos.prop$Treatment, levels=c("ETO", "DOC", "NCL","NCH","BFL","BFH"))

# Proportion data can be summarized by averaging
Mesos.Comb <- Mesos.prop %>% 
  group_by(Time.hr, Target, Size, Treatment) %>% 
  summarise(prop = mean(prop), Gc.mesocosm = mean(Gc.mesocosm)) 
#Set order of treatment variables
Mesos.Comb$Treatment = factor(Mesos.Comb$Treatment, levels=c("ETO", "DOC","NCL","NCH","BFL","BFH"))
```

Now, we run our statistical analyses.

```{r Stats}
#Change time to days, so that units for removal will be /day
Mesos <- Mesos %>% mutate(Time.days = Time.hr/24)

#Mixed-effect/hierarchical model, b.c. of repeated measures within mesocosms

mixed.mod <- lmer(LNGc.meso ~ Time.days:Treatment*Size*Target + 
                     (1 + Time.days|Meso.Num), data = Mesos, REML = FALSE)

#Examine residual plots
MixedResids <- resid_panel(mixed.mod, plots = "all")
MixedResids
#Response vs. Predicted is strong, and QQ plot looks fine. 
#Roughly normal distribution of residuals, although low outliers exist
shapiro.test(resid(mixed.mod)) # Shapiro test confirms this

ggsave(filename=paste0(plots.dir,"/MixedModelEval.png"), MixedResids, width = 8, height =6, units = c("in"))

#Model Summary
summary(mixed.mod)

#Export coefficients from the fixed portion of model
fixed_effects <- fixef(mixed.mod)
random_effects <- ranef(mixed.mod)$Meso.Num

# Look at model fit for each mesocosm
fit <- Mesos
fit$resids <- resid(mixed.mod)
fit <- fit %>% mutate(Conditional_Prediction = LNGc.meso - resids)
fit$Marginal_Prediction = predict(mixed.mod, re.form=NA)

# Plot
headernames <- c(
  `CARP` = "Carp",
  `STHD` = "Steelhead",
  `ETO` = str_wrap("No Leaves",15),
  `DOC` = str_wrap("Dissolved Organic Carbon",15),
  `NCH` = str_wrap("High Leaves",15),
  `NCL` = str_wrap("Low Leaves",15),
  `BFH` = str_wrap("High Leaves + Biofilm",15),
  `BFL` = str_wrap("Low Leaves + Biofilm",15),
  `1` = "Mesocosm 1",
  `2` = "Mesocosm 2",
  `3` = "Mesocosm 3",
  `4` = "Mesocosm 4"
)

Fit.plot.Carp <- ggplot(fit %>% subset(Target == "CARP"), aes(x=Time.hr, y=LNGc.meso, fill=interaction(Treatment,Size)))+
  geom_point(size=5, shape=21, stroke=0.75)+
  geom_line(aes(x = Time.hr, y = Conditional_Prediction, color=Size, linetype="dashed"))+
  theme_bw()+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_fill_manual(values=p9.5)+
  scale_color_manual(values=c("black","black"))+
  scale_linetype_manual(values=c("solid","dashed"))+
  ylab(expression(ln(eDNA~Gene~Copies~mesocosm^"-1")))+
  xlab(expression(Time~(hours)))+
  theme(axis.text.y=element_text(size=14,color="black"))+
  theme(axis.text.x=element_text(size=14,color="black"))+
  theme(axis.title.x=element_text(size=16,color="black"))+
  theme(axis.title.y=element_text(size=16,color="black"))+
  theme(legend.position="none")+
  scale_y_continuous(expand=c(0,0),limits=c(6,16), position = "right")+
  ###These lines facet the graph
  facet_grid(Treatment~Row, switch="y", labeller = as_labeller(headernames))+
  theme(strip.text.x = element_text(size=16),
        strip.text.y = element_text(size=16))+
  theme(strip.background =element_rect(fill="white"))+
  theme(panel.spacing = unit(1, "lines"))
#Add colors to facet grid
g <- facetColor(Fit.plot.Carp,c("#B7ECFF","#B7ECFF","#B7ECFF","#B7ECFF",p7))
ggsave(filename=paste0(plots.dir,"/ModelFit_Carp.png"), g, width = 14, height = 12, units = c("in"))

Fit.plot.Sthd <- ggplot(fit %>% subset(Target == "STHD"), aes(x=Time.hr, y=LNGc.meso, fill=interaction(Treatment,Size)))+
  geom_point(size=5, shape=21, stroke=0.75)+
  geom_line(aes(x = Time.hr, y = Conditional_Prediction, color=Size, linetype="dashed"))+
  theme_bw()+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_fill_manual(values=p9.5)+
  scale_color_manual(values=c("black","black"))+
  scale_linetype_manual(values=c("solid","dashed"))+
  ylab(expression(ln(eDNA~Gene~Copies~mesocosm^"-1")))+
  xlab(expression(Time~(hours)))+
  theme(axis.text.y=element_text(size=14,color="black"))+
  theme(axis.text.x=element_text(size=14,color="black"))+
  theme(axis.title.x=element_text(size=16,color="black"))+
  theme(axis.title.y=element_text(size=16,color="black"))+
  theme(legend.position="none")+
  scale_y_continuous(expand=c(0,0),limits=c(6,16), position = "right")+
  ###These lines facet the graph
  facet_grid(Treatment~Row, switch="y", labeller = as_labeller(headernames))+
  theme(strip.text.x = element_text(size=16),
        strip.text.y = element_text(size=16))+
  theme(strip.background =element_rect(fill="white"))+
  theme(panel.spacing = unit(1, "lines"))
#Add colors to facet grid
g <- facetColor(Fit.plot.Sthd,c("#E8CDE9","#E8CDE9","#E8CDE9","#E8CDE9",p7))
ggsave(filename=paste0(plots.dir,"/ModelFit_Sthd.png"), g, width = 14, height = 12, units = c("in"))

#Fits looks good

#Generate the data for Table 3
tab3 <- tidy(anova(mixed.mod1)) 
tab3


#The emtrends() function uses a difference quotient to estimate 
#the slope of a line fitted to a given variable.
# We apply emtrends to estimate the slope of "LN.Gc" according to the numerical covariate "Time.days"
# This gives us an estimate of removal (in /day) according to our categorical predictors (Treatment, eDNA particle size, and Target organism)

Treatment <- emtrends(mixed.mod1,"Treatment", var = "Time.days") 
Size <- emtrends(mixed.mod1,"Size", var = "Time.days") 
Target <- emtrends(mixed.mod1,"Target", var = "Time.days")
#Interactions are significant here, so be careful interpreting these results.
#In the text, we present these results simultaneously with the results from the
# full model, so as not to misrepresent the complexity of the interactions. 

#Save removal estimates for barplots
Treatment.Slopes <- as.data.frame(Treatment)
Size.Slopes <- as.data.frame(Size)
Target.Slopes <- as.data.frame(Target)

#Pairwise post-hoc (uses a Tukey by default). 
pairs(Treatment)
Treatment_pairwise <- pairs(Treatment) %>% as.data.frame()

pairs(Size)
Size_pairwise <- pairs(Size) %>% as.data.frame()

pairs(Target)
Target_pairwise <- pairs(Target) %>% as.data.frame()



#Separate by treatment and size
Treatment_Size <- emtrends(mixed.mod1, c("Treatment","Size"), var = "Time.days")
Treatment_Size

pairs(Treatment_Size, by="Size")
pairs(Treatment_Size, by="Treatment")

Treatment_Size.Slopes <- as.data.frame(Treatment_Size)

#Separate by size and target
Target_Size <- emtrends(mixed.mod1, c("Target", "Size"), var = "Time.days")
Target_Size
pairs(Target_Size)

Target_Size.Slopes <- as.data.frame(Target_Size)

#Separate by target and treatment
Target_Treatment <- emtrends(mixed.mod1, c("Target", "Treatment"), var = "Time.days")
Target_Treatment.Slopes <- as.data.frame(Target_Treatment)

pairs(Target_Treatment, by="Target")
pairs(Target_Treatment, by="Treatment")


#Lastly, look at removal based on all three factors
#Most accurate comparison due to interactions between the three. 
Final <- emtrends(mixed.mod1,c("Treatment","Size","Target"), var = "Time.days")
Final

Final.Slopes <- as.data.frame(Final)
Final.Slopes

#Pairwise Comparisons for D)
pairs(Final, by=c("Size","Target"))
plot(Final, by=c("Size","Target"), comparisons=T)

write.csv(Final.Slopes, file=paste0(files.dir,"/MesosRemovalMODEL.csv"), row.names=F)

```
