---
title: "Script (Data Compilation + Analysis)"
author: "Erik Curtis"
date: "2024-05-30"
output: html_document
---

# 1. Prepare Data

Here we clean our data and prepare dataframes/.csv files for statistical analysis. This section takes the raw data from the ddPCR plate files ("/Data" directory) and separates it into 4 .csv's

1.  LeafMesos-BKD.csv (Background samples from mesocosms pre-release)
2.   LeafMesos-Controls.csv (Field blanks, Extraction blanks, and +/- PCR controls)
3.  LeafMesos-ReleaseSolution.csv (eDNA source solution / buckets)
4.  LeafMesos-Mesoscosms.csv (the release data)

In addition, this script incorporates additional relevant data from the experiment, drawn from the "/Files" directory. This includes the volume of water filtered from each sample, as well as ancillary data (Temp, pH, water velocity, nutrient conc.,

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=objects())
this.dir = dirname(rstudioapi::getActiveDocumentContext()$path)
data.dir = paste0(this.dir,"/Data")
files.dir = paste0(this.dir,"/Files")
plots.dir = paste0(this.dir,"/Plots")
setwd(this.dir)

#Packages
library(dplyr)
library(ggpubr)
library(ggsci)
library(Rcpp)
library(reshape)
library(lubridate)
library(naniar)
library(gtools)
library(tidyr)
```

Here, we prepare the raw data (.csv files obtained from the ddPCR machine) for analysis. Positive and negative controls are separated from experimental data, and reactions that failed (i.e. not enough separation between positive and negative droplet clouds) are removed.

```{r Prep Data}
#Create a blank dataframe
Data.Full = data.frame(matrix(nrow= 0, ncol =0))

#Load Data into Data.Full
 
list = list.files(data.dir)
list <- mixedsort(sort(list))
for (i in 1:length(list)) {
  Data.Full <-rbind(Data.Full, read.csv(paste0(data.dir,"/",list[i]) , row.names = ) %>% mutate(Run = i))
}

#Remove unnecessary columns from Quantasoft outputs
Data.Full <- Data.Full %>% select(-c(2,3,5,7,9,11:14,17:21,23:41,43:63))

#Remove failed wells (identified manually by looking at 1-D plot in QuantaSoft)
#Failed reactions are identified by the plate number, and the well coordinates
failed.Rxns <- c("1.F01", "1.F02", "1.F03", "7.C02", "7.C02", "8.C07", "8.C08",
                 "8.C09", "8.F04", "8.F05", "8.F06", "8.C07", "8.C08", "8.C09",
                 "9.B10", "9.B11", "9.B12", "10.C01", "10.C02","10.C03", "10.G04",
                 "10.G05", "10.G06", "10.C10", "10.C11", "10.C12", "10.D10",
                 "10.D11", "10.D12", "14.E07", "14.E08", "14.E09", "16.A04",
                 "16.B04", "16.C04", "18.B06", "18.C05", "18.C06", "18.D06",
                 "18.E05", "18.H04", "16.A01", "16.A02", "16.A03", "16.B01",
                 "16.B02", "16.B03", "14.C07", "14.C08", "14.C09")  
Data.Full <- Data.Full %>% mutate(Run.ID = paste(as.character(Run),Well,sep="."))
Data.Full <- Data.Full %>% replace_with_na(list(Run.ID = failed.Rxns))
Data.Full <- Data.Full %>% na.omit()
Data.Full <- Data.Full %>% select(-c(11))


#Separate experimental data from negative and positive controls
#Information about each ddPCR reaction is encoded in "Sample"
Data.NC <- Data.Full %>% 
  subset(Sample != "Negative_CTL") %>% 
  subset(Sample!= "Positive_CTL") %>% 
  subset(substr(Sample,1,2) != "EB") %>% 
  subset(substr(Sample,1,2) != "CB")

Data.C <- Data.Full %>% 
  subset(Sample == "Negative_CTL" |
         Sample == "Positive_CTL" | 
         substr(Sample,1,2) == "EB" | 
         substr(Sample,1,2) == "CB")

#Data about the sample is encoded in its name

Data.NC <- Data.NC %>% 
  cbind(colsplit.character(Data.NC$Sample,
                           split="_", 
                           names = c("Meso.Num", "Time", "Size","Dilution")
                           )
        ) %>% 
  suppressWarnings()

#Separate the release solution from sample data

#BKT = Release Solution/Bucket Data
Data.BKT <- subset(Data.NC, Time == "CARP" | Time == "STHD") 
#NC = Not Control (i.e. sample data)
Data.NC <- subset(Data.NC, Time != "CARP" & Time != "STHD")

#Correct dilution factor for samples that were not diluted, replace with "1"
rem <- c("M1","M2","M3","M4","M5","M6",
         "M7","M8","M9","M10","M11","M12",
         "M13","M14","M15","M16","M17","M18",
         "M19","M20","M21","M22","M23","M24")
Data.NC <- Data.NC %>% 
  replace_with_na(list(Dilution = rem),"1x") 

x <- Data.NC %>% 
  subset(is.na(Dilution)) %>% 
  mutate(Dilution = "1")

Data.NC <- Data.NC %>% subset(!is.na(Dilution))
Data.NC <- rbind(Data.NC, x)
rm(x)

#Some samples were diluted prior to ddPCR, so we need to scale their concentration accordingly.
#We do this by multiplying by the dilution factor
Data.NC <- Data.NC %>% mutate(Concentration = Concentration * as.double(Dilution))

#Combining Technical Replicates

#We ran each mesocosm sample in triplicate, and we want to combine these 3 values into a single value for concentration. 
#We do this by summing the positive and negative droplets for all 3 ...

x <- Data.NC %>% 
  group_by(Sample, Target) %>% 
  summarize(Well = "*", 
            Target = first(Target),
            CopiesPer20uLWell = mean(CopiesPer20uLWell), 
            Positives = sum(Positives), 
            Negatives= sum(Negatives), 
            AcceptedDroplets = sum(AcceptedDroplets), 
            Threshold = mean(Threshold), 
            Run = first(Run), 
            Dilution = first(Dilution)
            ) %>% 
  suppressMessages()

#Now we calucate concentration from the PDF of the Poisson Distribution 
#Quantasoft applies this formula to each well to obtain the estimate for concentration; here we apply it to the sum of three wells
#In this formula, 0.000848 uL is the average volume of a droplet during ddPCR (Given by Quantasoft)
 
x <- x %>% 
  mutate(Concentration = -log(Negatives/AcceptedDroplets)/0.000848)
#Units for Concentration are gene copies per uL

#Separate "Sample" again and fix dilution
x <- x %>% 
  cbind(colsplit.character(x$Sample, 
                           split="_", 
                           names = c("Meso.Num", "Time", "Size")
                           ) 
        ) %>% 
  suppressWarnings()
x <- x[-c(15)]
x$Dilution <- as.numeric(x$Dilution)
x <- x %>%  mutate(Concentration = Concentration*Dilution)

#Recombine
Data.NC <- x

#Truncate concentration to 2 decimal places
Data.NC$Concentration <- Data.NC$Concentration %>% 
  round_any(accuracy = 0.01, f=floor)

#Filter out BKD samples

#BKD = Background data, i.e. samples taken prior to eDNA addition
Data.BKD <- Data.NC %>% subset(Time == "BKD")
#NC = Not Control (i.e. samples taken after eDNA addition)
Data.NC <- Data.NC %>% subset(Time != "BKD")


#Get volume filtered for each sample 
Vol.Filtered <- read.csv(paste0(files.dir,"/FilteredVolume.csv"))
Data.NC <- inner_join(Data.NC, Vol.Filtered, by=c('Meso.Num','Time','Size'))

#Calculate the eDNA conc. in the water sample (GC.mL) given the concentration in the ddPCR reaction (Concentration, in GC / uL)
#DNA from the sample is eluted in 50uL of buffer 
# 4uL of this eluted DNA is added to 16 uL supermix (20 uL total rxn mixture)
# After algebra, calculation is the following 

Data.NC <- Data.NC %>% 
  mutate(GC.mL = Concentration*250 /Vol.Filtered.mL)

#Get mesocosm volume + ancillary for each mesocosm
#This datasheet contains DOC, Temp, pH, turbidity, and most importantly, Mesocosm Volume for each time point
Vol.Meso <- read.csv(paste0(files.dir,"/AncillaryFULL.csv"))
Data.NC <- inner_join(Data.NC,Vol.Meso, by=c("Meso.Num","Time"))


#Multiply GC.mL (concentration data) with Mesocosm volumes to get total number of gene copies in each mesocosm (count data)
Data.NC <- Data.NC %>% mutate(Gc.mesocosm = GC.mL * Meso.Volume.mL)

#Now adjust for diluted samples in release solution data
Data.BKT <- Data.BKT %>% 
  dplyr::rename(Bucket = Meso.Num, Rel.soln = "Time")

X <- Data.BKT$Dilution
Data.BKT$Dilution <- X %>%
  replace(X == "BKT1"| X == "BKT2" | X =="BKT3" | X =="BKT4", "1")
rm(X)

#Adjust Concentration by dilution factor
Data.BKT <- Data.BKT %>% 
  mutate(Concentration = Concentration * as.double(Dilution))

#Ignore Carp in STHD buckets and Steelhead in Carp Buckets (usually below LOD anyway)
#Also remove run 15, samples needed diluting, positive cloud was too dense
Data.BKT <- Data.BKT %>% subset(Target == Rel.soln & Run != 15 & Run != 13)

#Calculate true concentration (Vol. Filtered was 100mL for every sample)
Data.BKT <- Data.BKT %>% mutate(GC.mL = (Concentration*1000)/(4*100))

#Export everything as .csv files to "Files" directory
?write.csv
write.csv(Data.BKD, paste0(files.dir,"/LeafMesos-BKD.csv"))
write.csv(Data.C, paste0(files.dir,"/LeafMesos-Controls.csv"))
write.csv(Data.BKT, paste0(files.dir,"/LeafMesos-ReleaseSolution.csv"))
write.csv(Data.NC, paste0(files.dir,"/LeafMesos-Mesoscosms.csv"))
```
